Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-10-17 2023/NUMTA/Full paper/NUMTA_2023_MCO.tex
R -> B f -> phi

\textbf{Remark}. The above method is based on the ISA  global search algorithm, which has an explicit geometric interpretation (see \cite{Strongin2000}). Using trial points, it is possible to design a minorant for the objective function $f(x)$. Then the value of characteristic, taken with the opposite sign, i.e. $-R(i)$, is the minimum value of the minorant in the interval $(x_{i-1}, x_i)$. Moreover, the point of a new trial $x^{p+1}$, computed according to (\ref{eq:26}), is carried out at the point, at which the minimum of the minorant is situated.

>>>>

\textbf{Remark}. The above method is based on the ISA  global search algorithm, which has an explicit geometric interpretation (see \cite{Strongin2000}). Using trial points, it is possible to design a minorant for the objective function $\varphi(x)$. Then the value of characteristic, taken with the opposite sign, i.e. $-B(i)$, is the minimum value of the minorant in the interval $(x_{i-1}, x_i)$. Moreover, the point of a new trial $x^{p+1}$, computed according to (\ref{eq:26}), is carried out at the point, at which the minimum of the minorant is situated.
